metric analysis

### 2021-05-29 metric_analysis.Rmd
Update metric_analysis.Rmd

# Fit a Random Forest for each variable
rc_all <- split(resist_combined, resist_combined$variable)
rf_all <- lapply(rc_all, function(x) 
  randomForest(trough_resistance ~ ., data = x[-1:-2], importance = TRUE)
)
imp_all <- lapply(rf_all, function(x) {
  imp <- as.data.frame(importance(x))
  imp$met_var <- rownames(imp)
  as_tibble(imp)
})
importance <- bind_rows(imp_all, .id = "variable")
```

>>>>

# Fit a Random Forest for each variable (across all treatment severities)
# Note the r.f. functions don't play well with tibbles, so change to data frame
rc_all <- split(as.data.frame(resist_combined), resist_combined$variable)
rf_all <- lapply(rc_all, function(x) 
  randomForest(trough_resistance ~ ., data = x[-1:-2], importance = TRUE)
)

# Importance metrics and partial plot data
import <- list()
partial <- list()
for(var in names(rf_all)) {
  mod <- rf_all[[var]]
  imp <- as.data.frame(importance(mod))
  imp$met_var <- rownames(imp)
  import[[var]] <- as_tibble(imp)

  impvar <- rownames(imp)[order(imp[, 1], decreasing = TRUE)]
  for (i in seq_along(impvar)) {
    pp <- partialPlot(mod, rc_all[[var]], impvar[i], plot = FALSE)
    partial[[paste(var, i)]] <- tibble(var = var, 
                                       met_var = impvar[i],
                                       x = pp$x, y = pp$y)
  }
}

import <- bind_rows(import, .id = "var")
ggplot(import, aes(met_var, `%IncMSE`)) + geom_col() +
  coord_flip() +
  facet_wrap(~var)

partial <- bind_rows(partial)
ggplot(bind_rows(partial), aes(x, y, color = var)) + 
  geom_line() + 
  facet_wrap(~var + met_var, scales = "free")
```
